For Induction-Induction, Induction is Enough

### 2019-11-11 paper/paper.tex
formalisation section

\todo{UIP, funext, rewrite rules, version of Agda.}

>>>>

Agda formalisation of Sections \ref{sec:theory_of_signatures} and
\ref{sec:ambroise} can be found at
\url{https://github.com/amblafont/UniversalII}. In addition to the features in
the previous section, this formalisation also uses equality reflection for some equalities, through rewriting pragmas\cite{cockxsprinkles}. This is purely for convenience, and in principle we could eliminate the instances of equality reflection via UIP and function extensionality.
